Bricking up and overgrowing backdoors in Intrusion Detection Systems

### 2019-09-08 ex2/paper/paper.tex

Independent of the origin of such patterns, they might be exploited for masquerading attacks and thus are clearly unwanted. The use of \gls{pdp} and \gls{ale} plots therefore provides a convenient possibility for analyzing \gls{ml} models.
\subsection{Pruning Techniques}
\subsubsection{Neural Network Pruning}
\subsubsection{Random Forest Pruning}
For intrusion detection decision tree based models or random forests of decision trees have been shown to usually achieve higher accuracy than multilayer perceptrons \todo{citation needed} and moreover they are generally faster to train and possibly more interpretable. For \glspl{nids} we thus consider the removal of backdoors from decision tree based models to be a more pressing issue than from multilayer perceptrons.

>>>>

Independent of the origin of such patterns, they might be exploited for masquerading attacks and thus are clearly unwanted. The use of \gls{pdp} and \gls{ale} plots therefore provides a convenient possibility for analyzing \gls{ml} models.
\subsection{Pruning Techniques}
\subsubsection{Neural Network Pruning}

\cite{gu_badnets:_2017} proposed pruning as a defense mechanism against backdoored \glspl{cnn}. They show that by removing neuron that are infrequently used from the last convolutional layer, potential backdoors can be removed. The rationale behind this is that some neurons specialize processing the regular samples while others focus on the backdoor. To our knowledge, these pruning defences have been applied to \glspl{cnn} but not to \glspl{mlp}, which are commonly used for \glspl{nids} \cite{meghdouri_analysis_2018}. We implement two variants of the pruning defense: We prune neurons in \begin{enumerate*}\item all layers \item only in the last layer \end{enumerate*} by their average activation. For this, we look at the value of the activation function (\gls{relu} in our case) in the corresponding layer and then prune the neurons by setting the weight and bias to 0 in the layer preceding the activation function.

\subsubsection{Random Forest Pruning}
For intrusion detection, decision tree based models or random forests of decision trees  usually achieve higher accuracy than \glspl{mlp} \cite{meghdouri_analysis_2018} and moreover they are generally faster to train and possibly more interpretable. For \glspl{nids} we thus consider the removal of backdoors from decision tree based models to be a more pressing issue than from \glspl{mlp}.
